DATA 621 - Business Analytics and Data Mining

### 2020-10-07 HW2/HW2-Group2.rmd
Highlight active URL in purple

---
title: "DATA 621 - Business Analytics and Data Mining"
subtitle: 'Fall 2020 - Group 2 - Homework #2'
author: Avraham Adler, Samantha Deokinanan, Amber Ferger, John Kellogg, Bryan
  Persaud, Jeff Shamp
date: "10/11/2020"
output:
  pdf_document: default
  html_document: default
---

>>>>

---
title: "DATA 621 - Business Analytics and Data Mining"
subtitle: 'Fall 2020 - Group 2 - Homework #2'
author: Avraham Adler, Samantha Deokinanan, Amber Ferger, John Kellogg, Bryan
  Persaud, Jeff Shamp
date: "10/11/2020"
output:
  pdf_document: default
  html_document: default
urlcolor: purple  
---
